### 2018-04-22 Sections/economics_of_the_quantum_internet.tex
Economics minor

The computational scaling function introduced previously expresses the power of a quantum computer in terms of its classical-equivalent runtime, or equivalently FLOPs. However, this may not be the metric of interest when considering a computers algorithmic power. In many situations, of far greater interest is the size of a problem instance that can be solved in a given timespan. For example, the FLOPs associated with solving an instance of a 3-\textsc{SAT} problem\index{3-SAT problem} grows exponentially with the number of clauses. When discussing the execution of this problem on a given computer, what we really want to know is how many clauses our device can cope with, rather than what the classical-equivalent runtime is.

This observation motivates us to re-parameterise the power of quantum computers in terms of the problem size of a given algorithm that can be solved. Employing the same methodology as for computational scaling functions, we define the \textit{problem size scaling function}, which relates the size of an algorithmic problem to it's classical equivalent runtime. Then equating the computational and problem size scaling function yields,

\begin{definition}[Problem size scaling function]\index{Problem size scaling functions}
The problem size scaling function relates the size of a problem instance, in some arbitrary metric, to its classical-equivalent runtime under a time-shared model,
\begin{align}
t = f_\text{size}(s).
\end{align}
Equating this with the computational scaling function yields,
\begin{align}
	n\cdot \chi_\text{sc}(n_\text{global}) = f_\text{size}(s).
\end{align}
Isolating the problem size yields,
\begin{align}
s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global})).
\end{align}
\end{definition}

@@

First let us consider the classical case of linear scaling functions (for both the computational and problem size scaling function),
\begin{align}
	f_\text{sc}(n) &= \alpha_\text{sc} n,\nonumber\\
	f_\text{size}(s) &= \alpha_\text{size} s.
\end{align}
Solving for the problem size simply yields,
\begin{align}
s &= \frac{n}{\alpha_\text{size}} \nonumber\\
&= O(1),
\end{align}
where $n$ is regarded as a constant, and $n_\text{global}$ is a variable parameter of the network. That is, the problem sizes of solvable instances is independent of the size of the external network with whom we are time-sharing. This is to be expected, since these scaling functions are typical of classical computers.

@@

For exponential scaling functions,
\begin{align}
f_\text{sc}(n) &= e^{\alpha_\text{sc}n},\nonumber\\
f_\text{size}(s) &= e^{\alpha_\text{size}s},
\end{align}
we obtain,
\begin{align}
s &= \log\left(n \frac{e^{\alpha_\text{sc}n_\text{global}}}{\alpha_\text{sc}n_\text{global}}\right) \nonumber\\
&= O(n_\text{global}),
\end{align}
demonstrating that the solvable problem size grows linearly with network size.

>>>>

The computational scaling function\index{Computational scaling functions} introduced previously expresses the power of a quantum computer in terms of its classical-equivalent runtime, or equivalently FLOPs\index{FLOPs}. However, this may not be the metric of interest when considering a computer's algorithmic power. In many situations, of far greater interest is the size of a problem\index{Problem size} instance that can be solved in a given timespan. For example, the FLOPs associated with solving an instance of a 3-\textsc{SAT} problem\index{3-SAT problem} grows exponentially with the number of clauses. When discussing the execution of this problem on a given computer, what we really want to know is how many clauses our device can cope with, rather than what the classical-equivalent runtime is.

This observation motivates us to re-parameterise the power of quantum computers in terms of the problem size of a given algorithm to be solved. Employing the same methodology as for computational scaling functions, we define the \textit{problem size scaling function}, which relates the size of an algorithmic problem to it's classical equivalent runtime. Then equating the computational and problem size scaling function yields,

\begin{definition}[Problem size scaling function]\index{Problem size scaling functions}
The problem size scaling function relates the size of a problem instance, in some arbitrary metric, to its classical-equivalent runtime under a time-shared model,
\begin{align}
t = f_\text{size}(s).
\end{align}
Equating this with the time-shared computational power yields,
\begin{align}
	n\cdot \chi_\text{sc}(n_\text{global}) = f_\text{size}(s).
\end{align}
Isolating the problem size yields,
\begin{align}
s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global})).
\end{align}
\end{definition}

@@

First let us consider the classical case of linear scaling functions (for both the computational and problem size scaling functions),
\begin{align}
	f_\text{sc}(n) &= \alpha_\text{sc} n,\nonumber\\
	f_\text{size}(s) &= \alpha_\text{size} s.
\end{align}
Solving for the problem size simply yields,
\begin{align}
s &= \frac{n}{\alpha_\text{size}} \nonumber\\
&= O(1),
\end{align}
where $n$ is regarded as a constant, and $n_\text{global}$ is a variable parameter of the network. That is, the problem sizes of solvable instances is independent of the size of the external network with whom we are time-sharing. This is to be expected, since these scaling functions are typical of classical computers.

@@

For exponential scaling functions,
\begin{align}
f_\text{sc}(n) &= e^{\alpha_\text{sc}n},\nonumber\\
f_\text{size}(s) &= e^{\alpha_\text{size}s},
\end{align}
we obtain,
\begin{align}
s &= \log\left(n \frac{e^{\alpha_\text{sc}n_\text{global}}}{\alpha_\text{sc}n_\text{global}}\right) \nonumber\\
&= O(n_\text{global}),
\end{align}
demonstrating that the solvable problem size grows linearly with network size. That is to say, waiting for a doubling in the external network's size will also double the size of a \textbf{BQP}-complete\index{\textbf{BQP}-complete} problem that can be solved in the same time.
